---
title: "P8105 Homework 6"
author: "Yihan Qiu"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(mgcv)
library(modelr)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

The code chunk below loads and cleans the data for regression analysis.

```{r}
birthweight_data =
  read_csv("p8105_hw6_data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex, levels = c(1, 2), labels = c("male", "female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian", "Puerto Rican", "Other", "Unknown")),
    malform = factor(malform, levels = c(0, 1), labels = c("absent", "present")),
    mrace = factor(mrace, levels = c(1, 2, 3, 4, 8), labels = c("White", "Black", "Asian", "Puerto Rican", "Other")))

map(.x = birthweight_data, ~sum(is.na(.x)))

birthweight_data
```

There is no missing value in this dataset.


The code chunk below proposes a model for regression.

```{r}
model_1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + malform + wtgain, data = birthweight_data)

broom::tidy(model_1)
```

The code chunk below shows a plot of model residuals against fitted values.

```{r}
birthweight_data %>%
  add_predictions(model_1) %>%
  add_residuals(model_1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(x = "fitted values", y = "residuals")
```

The code chunk below fits the other two models.

```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight_data)
broom::tidy(model_2)

model_3 = lm(bwt ~ bhead + blength + babysex +
               bhead * blength + bhead * babysex + blength * babysex +
               bhead * blength * babysex, data = birthweight_data)
broom::tidy(model_3)
```

The code chunk below makes the comparison of three models in terms of the cross-validated prediction error.

```{r}
set.seed(1)
cv = crossv_mc(birthweight_data, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>%
  mutate(
    model_1 = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + malform + wtgain, data = .x)),
    model_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex +
               bhead * blength + bhead * babysex + blength * babysex +
               bhead * blength * babysex, data = birthweight_data))) %>%
  mutate(rmse_model_1 = map2_dbl(.x = model_1, .y = test, ~rmse(model = .x, data = .y)),
         rmse_model_2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
         rmse_model_3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y)))

cv
```

The code chunk below looks at RMSE distributions of three models.

```{r}
cv %>%
  select(starts_with("rmse")) %>%
  pivot_longer(rmse_model_1:rmse_model_3,
               names_to = "model",
               values_to = "rmse",
               names_prefix = "rmse_") %>%
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
```

From the boxplot above, we can see that the model I proposed has the smallest predicion error overall, while the model using length at birth and gestational age as predictors has the largest error in general.


## Problem 2

The code chunk below downloads the 2017 Central Park Weather Data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The code chunk below draws 5000 bootstrap samples.

```{r}
bootstrap_df = weather_df %>%
  bootstrap(n = 5000, id = "strap_number")
```

The code chunk below produces estimates of R-squared for each bootstrap sample.

```{r}
r_squared = bootstrap_df %>%
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)
  ) %>%
  unnest(results) %>%
  select(strap_number, r.squared)
```

The code chunk below plots the distribution of estimates of R-squared.

```{r}
r_squared %>%
  ggplot(aes(r.squared)) +
  geom_density() +
  labs(title = "Distribution of R-squared estimates", x = "R-squared estimates")
```

From the plot above, we can see that the distribution of estimates of R-squared is approximately normal, with mean centered around 0.91.



The code chunk below constructs a 95% confidence interval for R-squared.

```{r}
r_squared %>%
  summarize(
    lower_bound = quantile(r.squared, 0.025),
    upper_bound = quantile(r.squared, 0.975)
  )
```

The 95% confidence interval for R-squared is (0.8939688, 0.9270405).


The code chunk below produces estimates of log(beta_0 * beta_1) for each bootstrap sample.

```{r}
log_beta0_beta1 = bootstrap_df %>%
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>%
  unnest(results) %>%
  select(strap_number, term, estimate) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>%
  rename(beta_0 = `(Intercept)`, beta_1 = tmin) %>%
  mutate(log_beta0_times_beta1 = log(beta_0 * beta_1))
```

The code chunk below plots the distribution of estimates of log(beta_0 * beta_1).

```{r}
log_beta0_beta1 %>%
  ggplot(aes(log_beta0_times_beta1)) +
  geom_density() +
  labs(
    title = "Distribution of estimates of log(beta_0 * beta_1)",
    x = "log(beta_0 * beta_1)",
  )
```

From the plot above, we can see that the distribution of estimates of  log(beta_0 * beta_1) is approximately normal, with mean centered around 2.02.


The code chunk below constructs a 95% confidence interval for log(beta_0 * beta_1).

```{r}
log_beta0_beta1 %>%
  summarize(
    lower_bound = quantile(log_beta0_times_beta1, 0.025),
    upper_bound = quantile(log_beta0_times_beta1, 0.975)
  )
```

The 95% confidence interval for log(beta_0 * beta_1) is (1.965633, 2.058469).

